Galois Characterization of Function Fields of \\ Transcendence Degree $1$ over Number Fields

### 2017-08-25 Master Thesis/synopsis.tex
'assures' > 'ensures'

Let $A\subset \operatorname{Spv}(K)$ be a closed set, $S\subset K$ finite, and let $U_S\cap A\neq\varnothing$. Assume there exists a point $v\in U_S\cap A$ which is not closed. Let $\overline{S}$ be the image of $S\subset \mathcal{O}_v$ in $k(v)$. If $\operatorname{char}k(v)=0$, then $R=\mathbb{Z}[\overline{S}]\subset k(v)$ is a subring that is not a field since $\overline{S}$ is finite. If $\operatorname{char} k(v)=p>0$, $k(v)/\mathbb{F}_p$ is not an algebraic extension, thus we can find an element $T\in k(v)$ which is transcendental over $\mathbb{F}_p$. In this case, $R=\mathbb{F}_p[T, \overline{S}]\subset k(v)$ is a subring that is not a field. In both cases, \cite{ZS60} VI, §4 Corollary 1 to Lemma guarantees the existence of a non-trivial valuation $\widetilde{v_1}\in\operatorname{Spv}k(v)$ with $\overline{S}\subset R\subset \mathcal{O}_{\widetilde{v_1}}$. By Lemma \ref{2.2-pre}, $\widetilde{v_1}$ corresponds to a valuation $v_1\in\operatorname{Spv}(K)$ with $S\subset \mathcal{O}_{v_1}\subsetneq \mathcal{O}_v$, i.e. $v_1\in \overline{\{v\}}\cap U_S$ and $\operatorname{rank}(v_1)>\operatorname{rank}(v)$. Repeating this process for $v_1$ and so on, we get a specialization chain of valuations in $U_S$:
\[\mathcal{O}_v\supsetneq \mathcal{O}_{v_1}\supsetneq\cdots \supsetneq\mathcal{O}_{v_n} \]
Since $K$ is assumed to be finite dimensional, Lemma \ref{rank-dimension-inequality} assures that this sequence ends with a closed point $v_n\in \overline{\{v\}}\cap U_S\subset A\cap U_S$.

>>>>

Let $A\subset \operatorname{Spv}(K)$ be a closed set, $S\subset K$ finite, and let $U_S\cap A\neq\varnothing$. Assume there exists a point $v\in U_S\cap A$ which is not closed. Let $\overline{S}$ be the image of $S\subset \mathcal{O}_v$ in $k(v)$. If $\operatorname{char}k(v)=0$, then $R=\mathbb{Z}[\overline{S}]\subset k(v)$ is a subring that is not a field since $\overline{S}$ is finite. If $\operatorname{char} k(v)=p>0$, $k(v)/\mathbb{F}_p$ is not an algebraic extension, thus we can find an element $T\in k(v)$ which is transcendental over $\mathbb{F}_p$. In this case, $R=\mathbb{F}_p[T, \overline{S}]\subset k(v)$ is a subring that is not a field. In both cases, \cite{ZS60} VI, §4 Corollary 1 to Lemma guarantees the existence of a non-trivial valuation $\widetilde{v_1}\in\operatorname{Spv}k(v)$ with $\overline{S}\subset R\subset \mathcal{O}_{\widetilde{v_1}}$. By Lemma \ref{2.2-pre}, $\widetilde{v_1}$ corresponds to a valuation $v_1\in\operatorname{Spv}(K)$ with $S\subset \mathcal{O}_{v_1}\subsetneq \mathcal{O}_v$, i.e. $v_1\in \overline{\{v\}}\cap U_S$ and $\operatorname{rank}(v_1)>\operatorname{rank}(v)$. Repeating this process for $v_1$ and so on, we get a specialization chain of valuations in $U_S$:
\[\mathcal{O}_v\supsetneq \mathcal{O}_{v_1}\supsetneq\cdots \supsetneq\mathcal{O}_{v_n} \]
Since $K$ is assumed to be finite dimensional, Lemma \ref{rank-dimension-inequality} ensures that this sequence ends with a closed point $v_n\in \overline{\{v\}}\cap U_S\subset A\cap U_S$.
